Software Product Line Analysis Techniques

### 2017-12-24 doc/quals/quals.tex
update

\title{Software Product Line Analysis Techniques}
\author{Ramy Shahin \\ rshahin@cs.toronto.edu}
\date{\today}                                           % Activate to display a given date or no date

@@

@@

>>>>

\title{Software Product Line Analysis Techniques}
\author{Ramy Shahin \\ rshahin@cs.toronto.edu}
\date{December 2, 2017}                                           % Activate to display a given date or no date

@@

In \cite{Classen:2013}, Labeled Transition Systems (LTSs) are extended with feature expressions into Featured Transition Systems (FTSs). FTSs can be used to encode variability-aware models, which can be checked by the SNIP model checker.

The paper provides a FTS-based formalism, together with model checking algorithms, complexity analysis (with proofs) and the featured LTL (fLTL) logic. Several state space reduction optimizations are also explained. The empirical evaluation highlights the speedup due to the optimized algorithm.

One shortcoming of this paper is that empirical evaluation is done on only one model (the mine pump controller model). This model is small compared to realistic models (only 457 FTS states), and the evaluation is done checking only 6 properties. With only one model (moreover, a small one), the evaluation results cannot be safely generalized.

@@

In \cite{Bodden:2013}, inter-procedural data flow analysis (based on the IFDS framework) is extended to annotative product lines. In IFDS, the data flow analysis problem is encoded as a graph reachability problem. Variability due to feature expressions is encod
